---
title: "Main figures: Amount and time exert independent influences on intertermporal choice"
output: html_notebook
---
Read in packages and subject IDs
"ind" is subjects with fitted k
"indET" is subjects with good eye tracking
"indETpat" is subjects with fitted k and good ET relative to indET
```{r}
#library(shiny)
wd=getwd()
setwd(wd) #Optional to set working directory where the data is
library(ggplot2)
library(ggsignif)
library(reshape2)
library(QuantPsyc)
library(effsize)
source("kendall.ci.R") #Load kendall.ci function***

#subjects
subjects=c(1:117);
#Exclude all patient: 16,23,45,46,50,65,78,79,86,99,101,110
sub_excl=c(1:15,17:22,24:44,47:49,51:64,66:77,80:85,87:98,100,102:109,111:117)
ind<-which(subjects %in% sub_excl) #non all patient subjects
#Subjects excluding bad eye tracking (validity<.5): 6,18,20,57,59,64,66,67,69,74,92,102
sub_ETexcl=c(1:5,7:17,19,21:56,58,60:63,65,68,70:73,75:91,93:101,103:117)
indET<-which(subjects %in% sub_ETexcl) #exclude bad eyetracking, but include all patient
indETpat<-which(sub_ETexcl %in% sub_excl) #Neither all patient nor bad eyetracking

subjects2=c(1:100);
#Exclude 2,3,4,10,14*,15,24,25*,41,45,51,54,55,56,67,75,86,91,94,98,100
# *are not all patient, they are just too noisy to fit
sub2_excl=c(1,5:9,11:13,16:23,26:40,42:44,46:50,52,53,57:66,68:74,76:85,87:90,92,93,95:97,99);
ind2<-which(subjects2 %in% sub2_excl) #non all patient subjects
#Subjects excluding bad eye tracking (validity<.5): 4,10,18,20,25,39,42,50,56,57,59,61,72,82,95 
sub2_ETexcl=c(1:3,5:9,11:17,19,21:24,26:38,40,41,43:49,51:55,58,60,62:71,73:81,83:94,96:100); 
indET2<-which(subjects2 %in% sub2_ETexcl) #exclude bad eyetracking, but include all patient
indETpat2<-which(sub2_ETexcl %in% sub2_excl) #Neither all patient nor bad eyetracking
```
Load data
```{r}
#kvals
alllogk<-read.table("allLogk.csv", header=FALSE, sep=",") 
alllogk2<-read.table("allLogk_rep.csv", header=FALSE, sep=",")
#ET indices
opt<-read.table("OptInd.csv", header=FALSE, sep=",") 
opt2<-read.table("OptInd_rep.csv", header=FALSE, sep=",")
payneInd<-read.table("PayneInd.csv", header=FALSE, sep=",") 
payneInd2<-read.table("PayneInd_rep.csv", header=FALSE, sep=",")
attInd<-read.table("AttInd.csv", header=FALSE, sep=",") 
attInd2<-read.table("AttInd_rep.csv", header=FALSE, sep=",")
firstFix<-read.table("firstFixes.csv", header=FALSE, sep=",") 
firstFix2<-read.table("firstFixes_rep.csv", header=FALSE, sep=",")

#DDM data
ddm<-read.table("attDDM.csv", header=FALSE, sep=",") 
ddm2<-read.table("attDDM_rep.csv", header=FALSE, sep=",")
ddm$driftDif=ddm$V1-ddm$V2
ddm2$driftDif=ddm2$V1-ddm2$V2
ddm$NDTdif=ddm$V3-ddm$V4
ddm2$NDTdif=ddm2$V3-ddm2$V4

#data frames
dfET=data.frame(ddm[indET,],opt,attInd,payneInd,firstFix)
colnames(dfET)<-c("driftA","driftT","NDTA","NDTT","Bounds","LL","BIC","AIC",
                  "difDrift","difNDT","optInd","attInd","payneInd","firstFix")
dfET$col<-"lightgray"
dfET$col[indETpat]<-"gray"
dfET$logk<-alllogk$V1[indET]
dfET2=data.frame(ddm2[indET2,],opt2,attInd2,payneInd2,firstFix2)
colnames(dfET2)<-c("driftA","driftT","NDTA","NDTT","Bounds","LL","BIC","AIC",
                  "difDrift","difNDT","optInd","attInd","payneInd","firstFix")
dfET2$col<-"lightgray"
dfET2$col[indETpat2]<-"gray"
dfET2$logk<-alllogk2$V1[indET2]

#RT
rt<-read.table("avgRT.csv", header=FALSE, sep=",") 
rt2<-read.table("avgRT_rep.csv", header=FALSE, sep=",")

#attribute wise DDM data frames
dfDDM=data.frame(rt$V1, ddm) 
colnames(dfDDM)<-c("rt","driftA","driftT","NDTA","NDTT","Bounds","LL","BIC","AIC","difDrift","difNDT")
dfDDM$logk=alllogk$V1
dfDDM$color="light gray"
dfDDM$color[ind]="gray"
dfDDM$meanLat=(dfDDM$NDTA+dfDDM$NDTT)/2
#Group 2
dfDDM2=data.frame(rt2$V1,ddm2)
colnames(dfDDM2)<-c("rt","driftA","driftT","NDTA","NDTT","Bounds","LL","BIC","AIC","difDrift","difNDT")
dfDDM2$logk=alllogk2$V1
dfDDM2$color="light gray"
dfDDM2$color[ind2]="gray"
dfDDM2$meanLat=(dfDDM2$NDTA+dfDDM2$NDTT)/2
#Option-wise DDM data frames
ddm_hyp<-read.table("optDDM.csv", header=FALSE, sep=",")
ddm_hyp$driftDif=log(ddm_hyp$V1)-log(ddm_hyp$V2)
ddm_hyp$NDTdif=ddm_hyp$V3-ddm_hyp$V4
dfDDM_hyp=data.frame(rt$V1,ddm_hyp)
colnames(dfDDM_hyp)<-c("rt","driftA","driftT","NDTA","NDTT","Bounds","LL","BIC","AIC","difDrift","difNDT")
dfDDM_hyp$logk=alllogk$V1
dfDDM_hyp$color="light gray"
dfDDM_hyp$color[ind]="gray"
dfDDM_hyp$meanLat=(dfDDM_hyp$NDTA+dfDDM_hyp$NDTT)/2
#Group2
ddm_hyp2<-read.table("optDDM_rep.csv", header=FALSE, sep=",")
ddm_hyp2$driftDif=log(ddm_hyp2$V1)-log(ddm_hyp2$V2)
ddm_hyp2$NDTdif=ddm_hyp2$V3-ddm_hyp2$V4
dfDDM_hyp2=data.frame(rt2$V1 ,ddm_hyp2)
colnames(dfDDM_hyp2)<-c("rt","driftA","driftT","NDTA","NDTT","Bounds","LL","BIC","AIC","difDrift","difNDT")
dfDDM_hyp2$logk=alllogk2$V1
dfDDM_hyp2$color="light gray"
dfDDM_hyp2$color[ind2]="gray"
dfDDM_hyp2$meanLat=(dfDDM_hyp2$NDTA+dfDDM_hyp2$NDTT)/2
#BIC data frames
dfBIC<-data.frame(dfDDM$BIC,dfDDM_hyp$BIC,dfDDM$logk)
colnames(dfBIC)<-c("attBIC","optBIC","logk")
dfBIC$dif<-dfBIC$attBIC-dfBIC$optBIC
dfBIC$col<-"gray80" #all patient are light gray
dfBIC$col[ind]<-"gray50" #regular are gray
dfBIC$col[which(dfBIC$dif>0)]<-"gray25" #option-wise better than attribute-wise is darker
dfBIC$shape<-dfDDM$color
#Group 2
dfBIC2<-data.frame(dfDDM2$BIC,dfDDM_hyp2$BIC,dfDDM2$logk)
colnames(dfBIC2)<-c("attBIC","optBIC","logk")
dfBIC2$dif<-dfBIC2$attBIC-dfBIC2$optBIC
dfBIC2$col<-"gray80" #all patient are light gray
dfBIC2$col[ind2]<-"gray50" #regular are gray
dfBIC2$col[which(dfBIC2$dif>0)]<-"gray25" #option-wise better than attribute-wise is darker
dfBIC2$shape<-dfDDM2$color
```
Figure 2 plot of difference in BIC by k for option-wise and attribute-wise DDM
```{r}
#Comparison of BIC's for attribute-wise vs. option-wise DDM
ggplot(dfBIC, aes(x=dif, y=logk)) + 
  geom_point(aes(color=col, shape=shape),size=2.5, alpha=.7)+
  guides(alpha=FALSE)+ylim(-9.5,0)+
  theme_bw()+scale_colour_grey(start=.1, end=.7)+
  scale_shape_manual(values=c(16,17))+
  scale_x_continuous(breaks=seq(-125,75,by=25), limits=c(-130,80))+
  theme(text=element_text(size=20),legend.position = "none",plot.margin=unit(c(.5,1,.5,.5),"cm"))+
  xlab("Attribute-wise - Option-wise BIC") +
  ylab("Log(k)") 
ggsave("DDM_BIC_logk.pdf",width=6.2,height=5)
cor.test(dfBIC$attBIC[ind]-dfBIC$optBIC[ind],dfBIC$logk[ind]) 
binom.test(sum(dfBIC$dif<0),length(dfBIC$dif),p=.5,alternative=c("two.sided"))

#Histogram
col=c(rep("gray50",13),rep("gray25",7))
ggplot(dfBIC, aes(x=dif))+theme_bw()+
  xlab("Attribute-wise - Option-wise BIC")+ylab("Count")+
  geom_histogram(breaks=seq(-130,70, by=10),fill=col, color="white")+
  theme(text=element_text(size=20))+ylim(0,35)+
  scale_x_continuous(breaks=seq(-125,75,by=25), limits=c(-130,80))
ggsave("DDM_BIC.pdf", width=5.5, height=4)

### Group 2
ggplot(dfBIC2, aes(x=dif, y=logk)) + 
  geom_point(aes(color=col, shape=shape),size=2.5, alpha=.7)+
  guides(alpha=FALSE)+ylim(-9.5,0)+
  theme_bw()+scale_colour_grey(start=.1, end=.7)+
  scale_shape_manual(values=c(16,17))+
  scale_x_continuous(breaks=seq(-125,75,by=25), limits=c(-130,80))+
  theme(text=element_text(size=20),legend.position = "none",plot.margin=unit(c(.5,1,.5,.5),"cm"))+
  xlab("Attribute-wise - Option-wise BIC") +
  ylab("Log(k)") 
ggsave("DDM_BIC_logk2.pdf",width=6.2,height=5)
cor.test(dfBIC2$attBIC[ind2]-dfBIC2$optBIC[ind2],dfBIC2$logk[ind2]) 
binom.test(sum(dfBIC2$dif<0),length(dfBIC2$col),p=.5,alternative=c("two.sided"))

#Histogram
col=c(rep("gray50",13),rep("gray25",7))
ggplot(dfBIC2, aes(x=dif))+theme_bw()+
  xlab("Attribute-wise - Option-wise BIC")+ylab("Count")+
  geom_histogram(breaks=seq(-130,70, by=10),fill=col, color="white")+
  theme(text=element_text(size=20))+ylim(0,35)+
  scale_x_continuous(breaks=seq(-125,75,by=25), limits=c(-130,80))
ggsave("DDM_BIC2.pdf", width=5.5, height=4)
```
Figure 3 plot of drift slopes, difference in drift slope by log(k), and difference in latency by log(k)
```{r}
#Correlation of drift slope amt and time for attribute-wise DDM
ggplot(dfDDM, aes(x=driftA, y=driftT)) +
  geom_jitter(aes(col=logk, alpha=.5),size=2.5, width=.001, height=.001) + 
  guides(alpha=FALSE)+xlim(-.001,.081)+ylim(-.001,.061)+
  scale_colour_gradientn(limits=c(-9.5,-.4), colors=rainbow(8)) + #for rainbow
  #scale_colour_gradient(low="gray10", high="gray80") + for grayscale
  theme_bw()+theme(text=element_text(size=20)) +
  xlab("Drift Slope Amount") + ylab("Drift Slope Time") 
 ggsave("driftA_driftT.pdf",width=6.5, height=5)
cor.test(dfDDM$driftA,dfDDM$driftT) 

# Corr drift slopes group 2
ggplot(dfDDM2, aes(x=driftA, y=driftT)) +
  geom_jitter(aes(col=logk, alpha=.5),size=2.5, width=.001, height=.001) + 
  guides(alpha=FALSE)+xlim(-.001,.081)+ylim(-.001,.061)+
  scale_colour_gradientn(limits=c(-9.5,-.4),colors=rainbow(8)) + #for rainbow
  #scale_colour_gradient(low="gray10", high="gray80") + for grayscale
  theme_bw()+ theme(text=element_text(size=20)) +
  xlab("Drift Slope Amount") + ylab("Drift Slope Time") 
ggsave("driftA_driftT2.pdf",width=6.5, height=5)
cor.test(dfDDM2$driftA,dfDDM2$driftT) 

#Cor of dif drift speeds vs. k
ggplot(dfDDM, aes(x=difDrift, y=logk)) +
  geom_point(aes(color=color, shape=color),size=2.5, alpha=.5)+
  guides(alpha=FALSE)+ theme_bw()+
  scale_colour_grey(start=.1, end=.6)+ ylim(-10,0)+
  scale_shape_manual(values=c(16,17))+
  theme(text=element_text(size=20),legend.position = "none",  plot.margin=unit(c(.5,1,.5,.5),"cm"))+
  scale_x_continuous(breaks=seq(-.04,.08,by=.02), limits=c(-.04,.08))+
  xlab("Drift Slope Amount - Drift Slope Time") +
  ylab("Log(k)") 
ggsave("difDrift_logK.pdf",width=6, height=5)
cor.test(dfDDM$difDrift[ind],dfDDM$logk[ind]) 

#Cor of dif drift speeds vs. k group 2
ggplot(dfDDM2, aes(x=difDrift, y=logk)) +
  geom_point(aes(color=color, shape=color),size=2.5, alpha=.5)+
  guides(alpha=FALSE)+theme_bw()+
  scale_colour_grey(start=.1, end=.6)+ylim(-10,0)+
  scale_shape_manual(values=c(16,17))+
  theme(text=element_text(size=20),legend.position = "none", plot.margin=unit(c(.5,1,.5,.5),"cm"))+
  scale_x_continuous(breaks=seq(-.04,.08,by=.02), limits=c(-.04,.08))+
  xlab("Drift Slope Amount - Drift Slope Time") +
  ylab("Log(k)") 
ggsave("difDrift_logK2.pdf",width=6, height=5)
cor.test(dfDDM2$difDrift[ind2],dfDDM2$logk[ind2]) 

#Cor dif attribute latency (*10 to get ms, /100 to get s) and log k
drift0<-which(dfDDM$driftA==0 | dfDDM$driftT==0)
latInd=setdiff(ind,drift0)
ggplot(dfDDM, aes(x=difNDT/100, y=logk)) + 
  geom_point(aes(color=color, shape=color),size=2.5, alpha=.5)+
  guides(alpha=FALSE)+xlim(-2,2)+ylim(-10,0)+
  theme_bw()+scale_colour_grey()+
  scale_shape_manual(values=c(16,17))+
  theme(text=element_text(size=20),legend.position = "none")+
  xlab("Amount latency - Time latency (s)") +
  ylab("Log(k)") 
ggsave("diflat_logK.pdf",width=5.6,height=5)
cor.test(dfDDM$difNDT[ind],dfDDM$logk[ind]) 
t.test(dfDDM$NDTA,dfDDM$NDTT,paired=TRUE) 
cohen.d(dfDDM$NDTA,dfDDM$NDTT, pooled=TRUE, paired=TRUE)

#Cor dif attribute latency (*10 to get ms) and log k Group 2
ggplot(dfDDM2, aes(x=difNDT/100, y=logk)) + 
  geom_point(aes(color=color, shape=color),size=2.5, alpha=.5)+
  guides(alpha=FALSE)+xlim(-2,2)+ylim(-10,0)+
  theme_bw()+scale_colour_grey()+
  scale_shape_manual(values=c(16,17))+
  theme(text=element_text(size=20),legend.position = "none")+
  xlab("Amount latency - Time latency (s)") +
  ylab("Log(k)") 
ggsave("diflat_logK2.pdf",width=5.6,height=5)
cor.test(dfDDM2$difNDT[ind2],dfDDM2$logk[ind2])
t.test(dfDDM2$NDTA,dfDDM2$NDTT,paired=TRUE)
cohen.d(dfDDM2$NDTA,dfDDM2$NDTT, pooled=TRUE, paired=TRUE)

#Correlation of bounds and logk
cor.test(dfDDM$Bounds[ind],dfDDM$logk[ind]) 
cor.test(dfDDM2$Bounds[ind2],dfDDM2$logk[ind2]) 
#Correlation of bounds and RT
cor.test(dfDDM$logk[ind],dfDDM$rt[ind])
cor.test(dfDDM2$logk[ind2],dfDDM2$rt[ind2]) 
```
Figure 4 plot of Attribute Index and Payne Index by dif drift slope
```{r}
ggplot(dfET, aes(x=difDrift, y=attInd)) +
  geom_point(size=2.5, alpha=.5)+
  guides(alpha=FALSE)+
  theme_bw()+xlim(-.04,.07)+ylim(-1,1)+
  scale_colour_grey()+
  scale_x_continuous(breaks=seq(-.04,.08,by=.02), limits=c(-.04,.08))+
  theme(text=element_text(size=20), plot.margin=unit(c(.5,1,.5,.5),"cm"))+
  xlab("Drift Slope Amount - Drift Slope Time") +
  ylab("Attribute index") 
ggsave("difDrift_att.pdf",width=5.8, height=5)
cor.test(dfET$logk[indETpat],dfET$attInd[indETpat]) 
cor.test(dfET$difDrift,dfET$attInd) 

#Cor attribute index and dif drift speeds group 2
ggplot(dfET2, aes(x=difDrift, y=attInd)) +
  geom_point(size=2.5, alpha=.5)+
  guides(alpha=FALSE)+
  theme_bw()+xlim(-.04,.07)+ylim(-1,1)+
  scale_colour_grey()+
  scale_x_continuous(breaks=seq(-.04,.08,by=.02), limits=c(-.04,.08))+
  theme(text=element_text(size=20), plot.margin=unit(c(.5,1,.5,.5),"cm"))+
  xlab("Drift Slope Amount - Drift Slope Time") +
  ylab("Attribute index") 
ggsave("difDrift_att2.pdf",width=5.8, height=5)
cor.test(dfET2$logk[indETpat2],dfET2$attInd[indETpat2]) 
cor.test(dfET2$difDrift,dfET2$attInd)

cor.test(dfET$optInd[indETpat],dfET$logk[indETpat]) 
cor.test(dfET2$optInd[indETpat2],dfET2$logk[indETpat2]) 

#Cor dif drift slopes and Payne index
ggplot(dfET, aes(x=difDrift, y=payneInd)) +
  geom_point(size=2.5, alpha=.5)+
  guides(alpha=FALSE)+
  theme_bw()+xlim(-.07,.07)+
  scale_colour_grey()+ylim(-1,1)+
  theme(text=element_text(size=20))+
  scale_x_continuous(breaks=seq(-.04,.08,by=.02), limits=c(-.04,.08))+
  xlab("Drift Slope Amount - Drift Slope Time") +
  ylab("Payne index") 
ggsave("difDrift_payne.pdf",width=5.7, height=5)
cor.test(dfET$logk[indETpat],dfET$payneInd[indETpat]) 
cor.test(dfET$difDrift,dfET$payneInd) 
cor.test(dfET$payneInd,dfET$attInd) 

#Cor dif drift slopes and Payne index Group 2
ggplot(dfET2, aes(x=difDrift, y=payneInd)) +
  geom_point(size=2.5, alpha=.5)+
  guides(alpha=FALSE)+
  theme_bw()+xlim(-.07,.07)+
  scale_colour_grey()+ylim(-1,1)+
  theme(text=element_text(size=20))+
  scale_x_continuous(breaks=seq(-.04,.08,by=.02), limits=c(-.04,.08))+
  xlab("Drift Slope Amount - Drift Slope Time") +
  ylab("Payne index") 
ggsave("difDrift_payne2.pdf",width=5.7, height=5)
cor.test(dfET2$logk[indETpat2],dfET2$payneInd[indETpat2]) 
cor.test(dfET2$difDrift,dfET2$payneInd) 
cor.test(dfET2$payneInd,dfET2$attInd) 

#First fixation is not normal--highly skewed distribution, so use kendall's tau instead
cor.test(dfDDM$difNDT[indET],firstFix$V1, method=c("kendall"))
kendall.ci(dfDDM$difNDT[indET],firstFix$V1)
cor.test(dfDDM2$difNDT[indET2],firstFix2$V1,method=c("kendall"))
kendall.ci(dfDDM2$difNDT[indET2],firstFix2$V1)
```